### 2019-08-22 README.Rmd
Re-knit README to reflect new ordering of diffEnrich results table
Bug fixes and knit Rmd with new plotFoldEnrichment function

The result of the *diffEnrich* call is the merged data frame with the estimated odds ration generated by the Fisher's Exact test 
and the associated p-value. Users can choose from those supported by *stats::p.adjust*, and the defualt is the False Discovery Rate (Benjamini and Hochberg).

>>>>

The result of the *diffEnrich* call is the merged data frame with the estimated odds ration generated by the Fisher's Exact test 
and the associated p-value. Users can choose from those supported by *stats::p.adjust*, and the default is the False Discovery Rate (Benjamini and Hochberg).

### Step 4: Plot fold enrichment

```{r plotFoldEnrichment}
## Plot fold enrichment
plotFoldEnrichment(de_res = diff_enrich, pval = 0.05, N = 5)
```
